Leadership across cultures and contexts: an exploratory analysis

### 2020-05-15 leadership_across_cultures_contexts.Rmd
Shortening intro

Leaders substantially shape group structures and outcomes. The structure of groups and their goals, in turn, as well as their subsistence strategies, can favor particular leader qualities. Despite decades of research and theorizing on leadership in numerous social science disciplines, to our knowledge there is no comprehensive or systematic investigation of leader functions and qualities, and the costs and benefits of leadership and followership, across a representative sample of nonindustrial societies. Moreover, outside of anthropology, most research and theorizing on leadership is based on data from Western or Westernized, postindustrial societies [@von_rueden_leadership_2015].

@@

Anthropology, on the other hand, has been criticized for exoticizing and essentializing the "Other" as part of its colonial history [@said1979; @abu2008; @reyes-garcia_small-scale_2017]. @abu2008 [p. 470], for instance, notes that

>culture is important to anthropology because the anthropological distinction between self and other rests on it. Culture is the essential tool for making other. As a professional discourse that elaborates on the meaning of culture in order to account for, explain, and understand cultural difference, anthropology also helps construct, produce, and maintain it. Anthropological discourse gives cultural difference (and the separation between groups of people it implies) the air of the self-evident. In this regard, the concept of culture operates much like its predecessor - race - even though in its twentieth-century form it has some important political advantages. Unlike race, and unlike even the nineteenth-century sense of culture as a synonym for civilization (contrasted to barbarism), the current concept allows for multiple rather than binary differences.

@@

Here we report the cluster analysis of variables that used the correlation distance metric ($1 - cor$), and the Ward agglomeration algorithm (for results from other methods, see the supplementary information). Figure \@ref(fig:cluster)A displays a dendrogram from the cluster analysis of the `r length(quality_vars)` leader quality variables and Figure \@ref(fig:cluster)B displays a dendrogram from the cluster analysis of the `r length(function_vars)` leader function variables. Each cluster analysis includes two estimates of significance for how strongly each cluster within the dendrogram is supported by the data. We rely on the AU (Approximately Unbiased) *p* values, which are computed by multiscale bootstrap resampling and represented as percentages (e.g., clusters with AU values $>95$ are strongly supported, and the top-level clusters are automatically highlighted by rectangles).

@@

>...a chief was a regulator, not an absolute ruler or tyrant. Although chiefs had considerable authority, their decisions were generally based on a consensus of opinion rather than arbitrary whim. The chief, like his celestial forebear, was supposed to be a guardian of the people, always mindful of their wishes and needs. And even though the office was hereditary in certain families, the man chosen to fill it had to demonstrate humility, generosity, and sagacity, because a jealous or aggressive temperament was considered unbefitting a chief.
<!-- nq18-015 -->

>>>>

Despite decades of research and theorizing on leadership in numerous social science disciplines, to our knowledge there is no comprehensive or systematic investigation of leader functions and qualities, and the costs and benefits of leadership and followership, across a representative sample of nonindustrial societies. Moreover, outside of anthropology, most research and theorizing on leadership is based on data from Western or Westernized, postindustrial societies [@von_rueden_leadership_2015].

@@

Anthropology, on the other hand, has been criticized for exoticizing and essentializing diverse "Others" as part of its colonial history [@said1979; @abu2008; @reyes-garcia_small-scale_2017]. @abu2008 [p. 470], for instance, notes that

>Anthropological discourse gives cultural difference (and the separation between groups of people it implies) the air of the self-evident. In this regard, the concept of culture operates much like its predecessor -- race -- even though in its twentieth-century form it has some important political advantages.

<!-- culture is important to anthropology because the anthropological distinction between self and other rests on it. Culture is the essential tool for making other. As a professional discourse that elaborates on the meaning of culture in order to account for, explain, and understand cultural difference, anthropology also helps construct, produce, and maintain it. Anthropological discourse gives cultural difference (and the separation between groups of people it implies) the air of the self-evident. In this regard, the concept of culture operates much like its predecessor - race - even though in its twentieth-century form it has some important political advantages. Unlike race, and unlike even the nineteenth-century sense of culture as a synonym for civilization (contrasted to barbarism), the current concept allows for multiple rather than binary differences. -->

@@

Here we report the cluster analysis of variables that used the correlation distance metric ($1 - cor$), and the Ward agglomeration algorithm (for results from other methods, see the supplementary information). Figure \@ref(fig:cluster)A displays a dendrogram from the cluster analysis of the `r length(quality_vars)` leader quality variables and Figure \@ref(fig:cluster)B displays a dendrogram from the cluster analysis of the `r length(function_vars)` leader function variables. Each cluster analysis includes two estimates of significance for how strongly each cluster within the dendrogram is supported by the data. We rely on the AU (Approximately Unbiased) *p* values, which are computed by multiscale bootstrap resampling and represented as percentages (e.g., clusters with AU values $\gt95$ are strongly supported, and the top-level clusters are automatically highlighted by rectangles).

@@

>...a chief was a regulator, not an absolute ruler or tyrant. Although chiefs had considerable authority, their decisions were generally based on a consensus of opinion rather than arbitrary whim. The chief, like his celestial forebear, was supposed to be a guardian of the people, always mindful of their wishes and needs. And even though the office was hereditary in certain families, the man chosen to fill it had to demonstrate humility, generosity, and sagacity, because a jealous or aggressive temperament was considered unbefitting a chief.
